# Introduction

To find the data set and Rmd file,  
- Go to github.com/mjw246 
- Click repositories  
- Click "R-Presentation"  
- Clone to Desktop  
- Add to your R library  
- Data set title is **MultipleLinearRegression** (even though it really isn't one)  
- Rmd file is called **Regressionpresentation.Rmd**

Download data frame
Set it as repository  
Something like below  

Make sure you don't set the "data" folder as the working directory!  

Then name it as...  
```{r}
nomoreg <- read.csv("data/MultipleLinearRegression.csv")
head(nomoreg)
```

Now you can see what the data frame looks like straight from the **.csv** file  
However, this is not R friendly for ggplot  
We need to do something MORE involving the *melt* function   

# "Melting" Your Data Set

First thing is to go into the console and type **?mark.data.frame**  
The key "argument" here is *id.vars* , which is a vector of id variables  
Create a new heading using the melt function  
BUT FIRST!! We have to open the "reshape2" package  
THEN we can create the "melted" data set  

```{r}
library(reshape2)
nomoregmelt <- melt(nomoreg,id.vars="Decibels")
head(nomoregmelt)
```

So now you see i've created 3 columns:  
- Decibels  
- variable (titled average minimum, average maximum, or average peak frequency)  
- value (the actual frequency values)  

Too see the entire data set now you just need to "View" nomoregmelt

# Making the Graph

First open ggplot 2

```{r}
library(ggplot2)
```
Then we create **regression graph 1**

```{r}
ggplot(nomoregmelt, aes(x=Decibels, y= value))+
  geom_point(shape=1)
```

Here i told r that our x values represent "Decibels"  
and that our y is the numbers from the "value" column in the melted data frame  

So now we've got all three sets of y values placed under one x value (Decibels) 

However, this is ugly, real ugly  
- Which set of data represents average peak frequency?    
- What do the points even mean?!  
- Wait, what does "value" mean??!  
- WHAT DOES ANY OF THIS MEAN???  

Calm down people, everything will be, just fine...   

Well, first thing we can do is change the color and shape of the points   
and then indicate which set of points represents which set of data  

```{r}
ggplot(nomoregmelt, aes(x=Decibels, y= value, colour=variable, shape=variable))+
  geom_point()
```

Ok, well this certainly an improvement

Now we've told R to make the color and shapes of the "variable" values different  
Remember that's why we made three columns from the "melted" data frame  
- Decibels = x values  
- value = frequency values, aka y values  
- variable = average minimum, maximum, and peak frequency  

Now the color and shape of the points are connected to "variable"  
You might also noticed that all these changes are in the first row of the ggplot script  
- "geom_point()" has nothing in the parenthesis

If we put something in the geom_point() then we get something like...


```{r}
ggplot(nomoregmelt, aes(x=Decibels, y= value, colour=variable, shape=variable))+
  geom_point(shape=1)
```

Putting the shape in the top row of the ggplot script sets stuff for the entire set of data frames  

ok back to the RIGHT way
```{r}
ggplot(nomoregmelt, aes(x=Decibels, y= value, colour=variable, shape=variable))+
  geom_point()
```

Now we need to change the name of "value" and "variable" to something that's less vague    

To do this we have to back to the original "nomoregmelt" script and change it  
We introduce two new arguments from **?mark.data.frame**   
- value.name  
- variable.name  

```{r}
nomoregmelt <- melt(nomoreg, id.vars="Decibels", value.name="Average Frequency", variable.name="Frequency")
```
now we plug these new values back into the ggplot script from before  
WHAT? value and variable are evolving!...

```{r}
ggplot(nomoregmelt, aes(x=Decibels, y= `Average Frequency`, colour=Frequency, shape=Frequency))+ geom_point()
```

value has evolved into Average Frequency AND  
variable has evolved into Frequency!  

Thus ends the value/variable title debacle  
And, thankfully, my terrible pokemon reference    

But there are few more things i'd like to do, like add trendlines 

```{r}
ggplot(nomoregmelt, aes(x=Decibels, y= `Average Frequency`, colour=Frequency, shape=Frequency))+ 
  geom_point()+
  geom_smooth(method=lm)
```

And last, let's get rid of the following:  
- Grey background  
- Major and minor gridlines  
- And let's make the axis lines black    

```{r}
ggplot(nomoregmelt, aes(x=Decibels, y= `Average Frequency`, colour=Frequency, shape=Frequency))+ 
  geom_point()+
  geom_smooth(method=lm)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
  panel.background = element_blank(), axis.line = element_line(colour = "black"))
```

And there you have it

# Questions

But there are still a couple of things wrong this graph...  
Things i do NOT know how to change...  

- First, how do you take the periods away from the frequency titles?
- Second, how do you get rid of "frequency" title and make a proper legend?



